---
title: "Udpipe playing"
author: "Fiona Adams"
date: "2/13/2020"
output: html_document
---

```{r} 
library(udpipe)
library(readtext)
library(corpus)
library(plyr)
library(dplyr)
```

```{r}
ud_model <- udpipe_download_model(language = "english")
udmodel_english <- udpipe_load_model(ud_model$file_model)

transcripts <- readtext("All_Transcripts/*.docx")

s <- udpipe_annotate(udmodel_english, transcripts$text[[1]])
x <- data.frame(s)
```
```{r}
x_adv <- x %>%
  filter(upos=="ADV")

#potentially: selectively keep some adverbs, but otherwise keep them out
table(x_adv$token)
```

```{r}
'%nin%' <- Negate('%in%')
x_stopwords <- x %>% 
  mutate(stopword = ifelse(lemma %nin% stopwords(), "NOT.STOPWORD", "STOPWORD"))
```

```{r}
x_filtered <- x_stopwords %>% 
  mutate(upos = as.character(upos)) %>%
  filter(., grepl('ADJ|ADV|INTJ|NOUN|PROPN|VERB', upos)) %>%
  subset(., nchar(as.character(lemma)) >= 3) %>%
  filter(., stopword != "STOPWORD")

table(x$upos)
table(x_filtered$upos)
```

```{r}
x_concatenated <- x_filtered %>%
  select(doc_id, sentence_id, token, upos) %>% 
  group_by(sentence_id, doc_id) %>% 
  summarise(text=paste(token,collapse=" ")) %>%
  filter(text != "Yeah")
```





UPOS: Universal part-of-speech tag.
```{r}
table(x$upos)
```
ADJ: adjective
ADP: adposition
ADV: adverb
AUX: auxiliary
CCONJ: coordinating conjunction
DET: determiner
INTJ: interjection
NOUN: noun
NUM: numeral
PART: particle
PRON: pronoun
PROPN: proper noun
PUNCT: punctuation
SCONJ: subordinating conjunction
SYM: symbol
VERB: verb
© 2014–2020 Universal Dependencies contributors. Site powered by Annodoc and brat.

GET RID OF:
-ADP / adpositions (prepositions and postpositions, ie during, into)
-*MAYBE* AUX: auxiliary (has, is, should, must)
-CCONJ: coordinating conjunction (and, or, but)
-DET: determiner (a, an, which, this)
-NUM: numeral (1, one)
-PART: particle (if only, let's, may you)
-*MAYBE* PRON: pronoun (you, everyone, nobody)
-PUNCT: punctuation (., !)
-SCONJ: subordinating conjunction (that, if, while)
-SYM: symbol (+, -)

KEEP:
-ADJ: adjective (big, old)
-*MAYBE* ADV: adverb (very, exactly, nowhere)
-INTJ: interjection (Yes!, Hello)
-NOUN: noun (girl, cat)
-PROPN: proper noun (Mary, NATO)
-VERB: verb (run, eat)


